FinalManuscript_DISCS_UG

### 2018-09-30 parts/01_introduction_02researchquestions.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

More specifically, our research will address the following sub-research questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
	\item Which homomorphic cryptosystems are the most secure under differential and entropy attacks?
\end{enumerate}

>>>>

More specifically, our research will address the following sub-questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations? 
\end{enumerate}

### 2018-09-30 parts/01_introduction_03objectives.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

>>>>

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

### 2018-09-30 parts/01_introduction_05scopeandlimitations.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis
        \begin{enumerate}
            \item Number of Pixel Change Rate (NPCR)
            \item Universal Average Change Intensity (UACI)
        \end{enumerate}
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item The Benlano cryptosystem~\cite{benaloh_dense_1994} which is a probabilistic cryptosystem which relies on the hardness of the discrete logarithm.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

### 2018-09-30 parts/02_relatedliterature.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

We first present an introduction to the concepts in cryptography, starting from the definition of a cryptosystem up to homomorphic encryption schemes, along with some examples from the literature. Then, we present some concepts in image processing, a suitable application of cryptography, specifically the common image operations used. Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.

\input{parts/02_relatedliterature_01homomorphiccryptosystems}
\input{parts/02_relatedliterature_02commonimageprocessingoperations}

\section{Related Work and Previous Implementations}
% CryptoImg

% example of homomorphic encryption / image manipulation past work

% minor limitation: improvement on previous work, but not a direct comparison

% major limitation: does not discuss security: are modified images also secure?

There has been work done regarding the application of homomorphic cryptosystems in image processing. In particular, Ziad, et al. introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}. This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem. Ziad, et al. also showed experimental results establishing the slow performance of image operations uner a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

However, a major limitation of \textit{CryptoImg} is that it does not consider image security. Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.

Furthermore, Ziad, et al. only presented a visual comparison and evaluation to establish the quality of the recovered images. We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.

This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosytems have yet to be implemented for image processing operations.

% HElib
Another related work would be the implementation of a fully homomorphic encryption. Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski-Gentry-Vaikuntanathan (BGV) homomorphic cryptosystem. This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.

>>>>

We begin with an overview of image processing, in which we define the image processing operations we are interested in
We first introduce concepts in cryptography and define homomorphic cryptosytems. along with some examples from the literature. Then, we present some concepts in , a suitable application of cryptography, specifically the common image operations used. Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.

\input{parts/02_relatedliterature_01commonimageprocessingoperations}
%facial recognition - theory
\input{parts/02_relatedliterature_02homomorphiccryptosystems}
\input{parts/02_relatedliterature_03partiallyhomomorphic}
\input{parts/02_relatedliterature_04fullyhomomorphic}
%facial recognition - implementation
\input{parts/02_relatedliterature_05previousimplementations}

### 2018-09-30 parts/02_relatedliterature_01commonimageprocessingoperations.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

\section{Common Image Operations}
In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations. These operations are performed on digital images. We can represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.

\subsection{Intensity Transformation}
To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

>>>>

\section{Common Image Operations}
In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations. We now present a list of basic operations performed on digital images.

We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.

\subsection{Intensity Transformations}
To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

### 2018-09-30 parts/02_relatedliterature_02homomorphiccryptosystems.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

\section{Homomorphic Cryptosystems}
% [include mention of metrics by which they are compared]

@@

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

@@

Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Some examples of homomorphic cryptosystems include the Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem~\cite{stern_public-key_1999}. Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic~\cite{li_elliptic_2012}. These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.

However, there exists \textit{fully homomorphic} cryptosystems, which are not limited to a fixed set of operations, but allow any arbitrary operations on the ciphertext. The first  fully homomorphic cryptosystem was presented by Gentry in 2009. Gentry's cryptosystem, which uses lattice-based cryptography, allows the computation of computation of arbitrary Boolean circuits on binary data~\cite{gentry_fully_2009, shortell_secure_2016}. New algorithms based on Gentry's initial ideas have since been made~\cite{ sen_homomorphic_2013}. One notable example is fully homomorphic cryptosystem by Smart and Vercauteren,~\cite{hutchison_fully_2010}, later improved by Gentry and Halevi ~\cite{hutchison_implementing_2011} which relies on cyclotomic number fields. In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings~\cite{dasgupta_design_2016}. These two cryptosytems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.

>>>>

\section{Homomorphic Cryptosystems}

@@

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

@@

Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.

%Homomorphic cryptosystems
%Some examples of homomorphic cryptosystems include the Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem~\cite{stern_public-key_1999}. Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic~\cite{li_elliptic_2012}. These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.

%However, there exists \textit{fully homomorphic} cryptosystems, which are not limited to a fixed set of operations, but allow any arbitrary operations on the ciphertext. The first  fully homomorphic cryptosystem was presented by Gentry in 2009. Gentry's cryptosystem, which uses lattice-based cryptography, allows the computation of computation of arbitrary Boolean circuits on binary data~\cite{gentry_fully_2009, shortell_secure_2016}. New algorithms based on Gentry's initial ideas have since been made~\cite{ sen_homomorphic_2013}. One notable example is fully homomorphic cryptosystem by Smart and Vercauteren,~\cite{hutchison_fully_2010}, later improved by Gentry and Halevi ~\cite{hutchison_implementing_2011} which relies on cyclotomic number fields. In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings~\cite{dasgupta_design_2016}. These two cryptosytems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.

### 2018-09-30 parts/02_relatedliterature_03partiallyhomomorphic.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

%\section{Introduction to the Appendices}

%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume. These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
\section{The Pallier cryptosystem}
The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
\subsection{Key generation, encryption and decryption algorithms}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\subsection{Homomorphic properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

@@

\section{The Benaloh cryptosystem}
The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. It relies on the hardness of the \textit{discrete logarithm problem}. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

\subsection{Key generation, encryption and decryption algorithms}
We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
\begin{itemize}
  \item $r$ divides $(p-1)$;
  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
  \item $\mathrm{gcd}(r,q-1)=1$.
\end{itemize}
Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
\begin{itemize}
  \item $y^{\phi/r}\neq 1 \bmod n$;
  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
\end{itemize}
We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

@@

\subsection{Homomorphic properties}
Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}

@@

\section{Dasgupta-Pal cryptosystem}
The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{n}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
\subsection{Key generation, encryption and decryption algorithms}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k$ be a prime number with $\ell$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$

As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
To eliminate noise from a polynomial ciphertext, the following refresh function is used.
\begin{align*}
	R(c(x)) = c(x) \bmod R_k
\end{align*}

\subsection{Homomorphic properties}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}

>>>>

\section{Partially homomorphic cryptosystems}

In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Pallier cryptosystem and the Benaloh cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

We will then show that the cryptosystems can be modified to support limited polynomial evaluation: given an encrypted message $m$, evaluate

These operations
\subsection{The Pallier cryptosystem}
The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Pallier cryptosystem and its homomorphic properties.

\subsubsection{Pallier cryptosystem description}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\subsubsection{Homomorphic Properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

@@

\subsection{The Benaloh cryptosystem}
The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

\subsubsection{Benaloh cryptosystem description}
We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
\begin{itemize}
  \item $r$ divides $(p-1)$;
  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
  \item $\mathrm{gcd}(r,q-1)=1$.
\end{itemize}
Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
\begin{itemize}
  \item $y^{\phi/r}\neq 1 \bmod n$;
  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
\end{itemize}
We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

@@

\subsubsection{Homomorphic Properties}
Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}

@@

Similar to the Paillier cryptosystem, we can include $m^2$ and $E(m^2)$ in the transmitted message

### 2018-09-30 parts/03_methodology.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

\subsection{Evaluating Cryptographic Security}
After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in~\cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
\begin{description}
	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in~\cite{bauer_information_2005} as
	\begin{align}
		H(X) = - \sum_{a:p_X(a)>0}{p_X(a)\log_2{p_X(a)}}
	\end{align}
	where $p_X(a)$ denotes the probability that the random variable $X$ takes on the value $a$.
	In the analysis of image encryption, $H(X)$ is computed for the values of the ciphertext pixels. To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values~\cite{ahmed_benchmark_2016}.

    We will compute $H(\mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image. Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
	\item [Correlation coefficient analysis (CC).]
		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in~\cite{ahmed_benchmark_2016} by:
		\begin{align}
            \mathrm{CC}(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
		\end{align}
		where
		\begin{itemize}
			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
		\end{itemize}

        For every $\mathrm{CDT}$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
	\item [NPCR and UACI.]
		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.

		On the other hand, the Universal Average Change Intensity (UACI) measures the average difference in pixel intensity between two images.

		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in~\cite{wu_npcr_2011} as
		\begin{align}
            \mathrm{NPCR}(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
            \mathrm{UACI}(X,Y) &= \frac{1}{L_{\max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
		\end{align}
		where
		\begin{itemize}
			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
			\item $D$ is a difference function between pixels $A$ and $B$ defined by
			\begin{align}
				D(A,B) =
				\begin{cases}
					0 &  \text{if $A = B$},\\
					1 &  \text{if $A \neq B$};
				\end{cases}
			\end{align}
		\item $L_{\max}$ is the maximum intensity of a pixel;
		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
		\end{itemize}
        We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem. A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks~\cite{ahmed_benchmark_2016}. Critical values for NPCR and UACI for given image sizes and bit depths are given in~\cite{wu_npcr_2011}.
\end{description}

@@

In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

>>>>

@@

In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}
